### 2022-07-25 analysis/peer_review_manuscript_1/1/reply-reviewer_2-1.Rmd

**A50:** We appreciate this suggestion as we also think that further discussions on this proposed gradient are useful.  
Indeed, we have elaborated this point further (and added additional remarks and suggestions regarding uncertainty handling) in a companion manuscript intended as a reply to @Hodgkins.2018 (this manuscript was written before @Verbeke.2022 was published). This reply manuscript is not yet published, since we first wanted to publish the manuscript discussed here which represents the technical basis for our reply manuscript. However, the script for the reply manuscript (containing also the text) is available via the reproducible research compendium to the manuscript discussed here.  
In brief, the results differ if the modified models are used due to the strong underestimation of Klason lignin contents (i.e. Klason lignin contents are strongly underestimated in @Hodgkins.2018). As a consequence, also the depth-related relative accumulation of Klason lignin during decomposition is probably underestimated. We think that this is an important finding since a larger amount of Klason lignin is required according to the modified models for the hypothesized stability of tropical peat and deeper peat than has been suggested.  
Another point is that because of the bias in the models, the original results can only be interpreted in terms of qualitative concepts for carbohydrates and aromatics which makes it much more difficult to connect the results to other studies, to generalize them, and to test them.  
To foreshadow more explicitly that we are preparing such an analysis, we modified the sentence (new: l. 496): "Results from currently published studies using the original models should be interpreted with caution (we are currently preparing a manuscript, see @Teickner.2022b, which explores the implications of our results here for the results of @Hodgkins.2018)."

--------------------------------------------

> **Q51:** "L466 Delete “, also in practice”."

**A51:** We changed the text as suggested (new: l. 500).

--------------------------------------------

## Supplementary Information

> **Q52:** "A general comment on the information here: apart from the introductory paragraphs to S1
and S2, there is a description of the figure followed by the legend to the figure and often
the material is a repeat. Really, it would be better just to have a descriptive legend."

**A52:** Thank you for making this suggestion. We changd the text as suggested.

--------------------------------------------

> **Q53:** "S1 Replace “as baseline” with “as a baseline”."

**A53:** Thank you. We changed the text as suggested.

--------------------------------------------

> **Q54:** "Figure 3. See same comment as for Figure 2 above."

**A54:** Thank you. We changed the figure as suggested (new: Fig. S3).

--------------------------------------------

> **Q55:** "Figure 4. The axis labels for (a) are the wrong way round! For “Sample type” is this the same as “class” in the main text? If so change to “class” (but see on Figure 11 below)."

**A55:** Thank you for pointing out this error. The axes labels are indeed the wrong way round. "Sample type" is not the same as "class" (the two classes defined in the manuscript text) in the main text. We changed the figure as suggested (new: Fig. S4).

--------------------------------------------

> **Q56:** "Figure 6. Replace “overestimation” with “underestimation” and “underestimation” with
“overestimation”."

**A56:** Thank you for pointing out this error. We changed the caption as suggested (new: Fig. S6).

--------------------------------------------

> **Q57:** "Figure 8. I would suggest having Training, Peat and Vegetation across the top and peak
heights down the side (as laid out in Figure 7). Also (a) and (b) seem to show the same
data; can this be right? In the legend it says peat (second row) but it is actually peat in
the third row."

**A57:** Thank you for spotting this error! Indeed, (a) did not show the data for the intensity at 3400 cm$^{-1}$, but for 1250 cm$^{-1}$. We corrected this and also changed the figure as suggested (new: Fig. S8).

--------------------------------------------

> **Q58:**  "Figure 10. Replace “6.31e-16” with “0”."

**A58:** Thank you! We changed the figure as suggested (new: Fig. S10).

--------------------------------------------

> **Q58:**  "Figure 11. Replace “type 2” with “class 2”. It is unclear what these classes are, and where does paper and cardboard fit in? Perhaps indicate in the list of sample types which are class 1, 2, 3, etc."

**A58:** Thank you. Since this text is deleted (see A52), we did not change the text. However, it is true that this was not described clearly enough and we think that this might also be relevant for the misunderstanding (we assume) for Q37. We hope that this comment was addressed in A37.

--------------------------------------------

> **Q59:** "Figure 12. The order of regressions mentioned in the description is not the same order as actually depicted. In the legend, replace “binnes” with “binned”, “50” with “20” (I presume), and “line” with “lines”."

**A59:** Thank you for pointing out these errors. We changed the caption as suggested (new: Fig. S12).

--------------------------------------------

> **Q60:** "Figure 13. The “Dataset” key could be omitted – it is superfluous."

**A60:** Thank you for the suggestion. It is true that the key is redundant. However, we would like to keep the redundancy here since the color scheme is applied across different figures and we think that this helps recognizing the different dataset types. If you think this is not only superfluous, but even confusing, we will remove the key here.

--------------------------------------------

```{r child="reply-additional.Rmd"}
```

## References
